\chapter*{Summary\markboth{\MakeUppercase{Summary}}{}}

The Large Hadron Collider is the first particle accelerator which is capable of providing an abundant amount of top-quark pair events at record-breaking centre-of-mass energies, allowing for a thorough investigation of physics at the TeV scale.
The data collected by the CMS detector during the 2012 run of the LHC is considered in this thesis and the event signature of interest corresponds to the semi-muonic decay of top-quark pair events.
These events have been used to determine whether the top-quark decay vertex is described purely by a left-handed vector coupling, as predicted by the Standard Model of elementary particle physics, or whether additional couplings occur due to new-physics phenomena. In this thesis the focus was on the estimation of the right-handed tensor coupling, denoted as $\gR$.

The study discussed in this thesis is the first direct measurement of the right-handed anomalous tensor coupling of the top-quark decay vertex.
It has been performed using a Matrix Element method, which is capable of extracting potentially the best estimate of any theoretical parameter from a sample of experimental events.
This advanced analysis technique evaluates each event and calculate a corresponding event probability using a dedicated phase-space integration.
%As a result, applying such a Matrix Element method requires a significant computing time such that 
It has been opted to apply a stringent event selection by for instance exploiting the specific characteristics of the b-quark jets in order to improve the reconstruction efficiency.
Two such jets are expected in top-quark pair events since the top-quark decays almost exclusively into a b-quark and a W-boson. 
%Since this reduces the number of selected events that will be processed by the phase-space integrator the required processing time is also seriously decreased.
%In addition, the number of selected events used in the analysis are reduced implying that also the 

With $19.6 \fbI$ of collision data taken at a centre-of-mass energy of $8 \TeV$ a right-handed tensor coupling value of
\begin{equation}
 \gR = -0.0071 \, \pm \, 0.0083 \, (\textrm{stat.}) \, \pm \, 0.0134  \, (\textrm{syst.}) = -0.0071 \, \pm \, \nonumber 0.0160
\end{equation}
was measured, which is consistent with the prediction of the Standard Model ($\gR$ = 0).
Comparing the obtained result with the currently existing exclusion limits for this right-handed tensor coupling also indicates an excellent agreement.
Hence it can be concluded that the Matrix Element method has been successfully applied on the reconstructed collision events recorded by the CMS experiment and has resulted in a rather accurate and first direct measurement of this anomalous coupling coefficient $\gR$.